A Search for Circumstellar Companions Around Nearby White Dwarf Sirius b

### 2021-07-20 paper/paper.tex
update paper

For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of L.A.Cosmic \citep{dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We finally remove sky background using a high-pass median filter. Each frame is co-registered and aligned with the center of the FOV and lastly cropped to the inner 200 pixels. With the pixel scale of \SI{10}{mas\per px} the crop corresponds to a maximum separation of \SI{2.7}{\au}. We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}.

We apply the technique of angular differential imaging \citep[ADI;][]{marois_angular_2006} where we disable the field rotator and allow the FOV to rotate throughout the night as Earth rotates. This apparent rotation isolates systematic noise from the telescope, which includes the point-spread function (PSF). By modeling and subtracting the PSF before derotating the frames to a common direction, potential companion signal is preserved since it does not appear stationary in the

@@

>>>>

For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of L.A.Cosmic \citep{dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We finally remove sky background using a high-pass median filter. At this point frames were manually filtered to remove bad frames, especially those with diffraction spikes like in \autoref{fig:spike}. Then, each good frame is co-registered using cross-correlations \citep{guizar-sicairos_efficient_2008} and aligned with the center of the FOV. Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch. With the pixel scale of \SI{10}{mas\per px} the crop corresponds to a maximum separation of \SI{2.7}{\au}. We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}.

During observing we applied the technique of angular differential imaging \citep[ADI;][]{marois_angular_2006} where we disable the field rotator and allow the FOV to rotate throughout the night along with Earth. The point-spread function (PSF), which is an instrumental effect, will not appear to rotate while any potential companion will appear to rotate. This allows modeling and subtracting the PSF with less probability for subtracting companion signal. After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.

For this analysis we used three statistical models for modeling the stellar PSF, classic median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA;][]{soummer_detection_2012}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}. The median subtraction and PCA methods were also applied in an annular method, where we model the PSF in annuli of increasing separation, since each annulus has similar statistcal properties under the framework of ADI \citep{marois_angular_2006}.

We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) detection map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020}. These metrics assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics. The SLIM map is an ensemble statistic which calculates the average STIM map from many residual cubes, such as many variations of PCA with differing number of components.

Another metric we calculate for some of the algorithms is the contrast curve, which determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above. We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.

@@

The flat residual images from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian S/N maps and STIM maps. The best performing algorithms for each epoch in terms of sensitivity were median subtraction median subtraction, and PCA subtraction with 2 principal components. For each epoch we determined there was not significant evidence for a companion around Sirius b.
